Influence of Connectivity on Dung Beetle Communities

### 2025-02-26 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
figures and tables

@@

>>>>

```{r GlobalOptions, include = FALSE}
options(knitr.duplicate.label = 'allow')
```

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(here)
library(tidyverse)
library(kableExtra)
# library(gridExtra)
# library(egg)
# library(magick)
# library(citr)
# library(devtools)
# devtools::install_github("crsh/papaja")
```

@@

```{r Table1, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

btl_data<-read_csv(here("corridor_docs","eric_ms_thesis","ms_data","data_clean","clean_btl_counts.csv"))
spp_codes<-read_csv(here("corridor_docs","eric_ms_thesis","ms_data","data_raw","species_codes.csv"))

btl_order<-btl_data %>%
  pivot_longer(pvin:ostr,names_to = "species",values_to = "n") %>% 
  group_by(species) %>%
  summarize(n=sum(n, na.rm=TRUE)) %>%
  arrange(desc(n)) %>%
  mutate(species = reorder(species, desc(n))) %>% 
  rename(sp_code=species)

btl_sums_patch<-btl_data %>%
  pivot_longer(pvin:ostr,names_to = "species",values_to = "n") %>% 
  group_by(species,patch) %>%
  summarize(n=sum(n, na.rm=TRUE)) %>%
  arrange(patch,desc(n)) %>% 
  rename(sp_code=species,
         n_patch=n) %>% 
  pivot_wider(
    names_from = patch,
    values_from = c(n_patch))

btl_order<-full_join(btl_order,btl_sums_patch,by="sp_code")

spp_table<-btl_order %>% 
  left_join(spp_codes,by="sp_code") %>% 
  unite("species",genus:species, sep=" ") %>% 
  mutate(species=if_else(sp_code=="ap*", "Aphodius spp.",species)) %>% 
  mutate(c=case_when(
  c == 0 ~ " ",
  c > 0 ~ "x",
  .default = as.character(c)
)) %>% 
  mutate(m=case_when(
  m == 0 ~ " ",
  m > 0 ~ "x",
  .default = as.character(m)
)) %>% 
  mutate(r=case_when(
  r == 0 ~ " ",
  r > 0 ~ "x",
  .default = as.character(r)
)) %>% 
mutate(w=case_when(
  w == 0 ~ " ",
  w > 0 ~ "x",
  .default = as.character(w)
)) %>% 
  select(species,n,m,c,w,r) %>% 
  rename(Species=species,
         N=n,
         Matrix=m,
         Corridor=c,
         Winged=w,
         Rectangular=r)

spp_table<-knitr::kable(spp_table, 
      digits = 2,
      align="lrcccc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Dung beetle species sampled in the SRS site and their total abundance over the course of the study.") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options="scale_down",
                font_size = 12,
                position = "left") %>% 
  column_spec(1, italic = T) %>% 
  row_spec(0, bold = T) %>% 
  row_spec(1:15, hline_after = T) 
spp_table
```

```{r Table2, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

btl_data<-read_csv(here("corridor_docs","eric_ms_thesis","ms_data","data_clean","clean_btl_counts.csv"))
spp_codes<-read_csv(here("corridor_docs","eric_ms_thesis","ms_data","data_raw","species_codes.csv"))

```
